### 2017-04-01 paper/modes.tex
Change example in section II
pass on paragraph example in section 2

The configuration \Seq{} is a proper fit for short-running test suites
since this is the default configuration and the execution provides
feedback in an acceptable time. However, for costly suites, it is
impractical for developers to wait long-running executions to take
action.  In this scenario, the remaining configuration may help to
amortize the execution cost depending on how the test suite was
designed. For instance, the configuration \SeqClassParMeth{} may
speedup the execution of test suites composed large test classes since
the cost of running all test methods is amortized by a pool of
threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes. Notice that both
configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
data-race condition at different levels. \Luis{This is wrong $\rightarrow$} 
For instance, if two test classes performs I/O operations to the same file,
the configuration \SeqClassParMeth{} would be preferable. Finally, 
the configuration \ParClassParMeth{} does not impose any sequential 
execution but it is more likely to manifest data-races as methods 
from different classes run in parallel.

@@

\subsubsection*{Illustration}~Figure~\ref{fig:surefire} illustrates
the support of parallel execution with the configuration
\ForkParMeth{} on Maven, a popular build system in Java projects.
Maven uses a configuration file based on XML (known as \pomf{}) to
define tasks related to the project building and these tasks are
performed several plugins. \Jbc{falar do surefire e explicar a
configuracao ilustrada - Surefire levanta uma JVM por core e cria uma
pool de 5 threads em cada JVM para executar testes em paralelo.}

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Maven setup with the configuration
    \ForkParMeth{}.  Maven forks one JVM per core (\CodeIn{forkCount}
    parameter) and uses five threads (\CodeIn{threadCount} parameter)
    to run methods (\CodeIn{parallel} parameter) within each JVM.}
\end{figure}

>>>>

The configuration \Seq{} is a proper fit for short-running test suites
since this is the default configuration and the execution provides
feedback in an acceptable time. However, for costly suites, it is
impractical for developers to wait long-running executions to take
action.  In this scenario, the remaining configuration may help to
amortize the execution cost depending on how the test suite was
designed. For instance, the configuration \SeqClassParMeth{} may
speedup the execution of test suites composed large test classes since
the cost of running all test methods is amortized by a pool of
threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes. Notice that both
configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
data-race condition at different levels. For instance, if two test methods performs operations in a same variable, the configuration \SeqClassParMeth{} would be preferable. Finally, 
the configuration \ParClassParMeth{} does not impose any sequential 
execution but it is more likely to manifest data-races as methods 
from different classes run in parallel.

@@

%%  to
%% define tasks related to the project building and these tasks are
%% performed several plugins.This file
%% contains defintions of tasks, which are implemented by a collection of
%% plugins.

%% \Jbc{falar do surefire e explicar a
%% configuracao ilustrada - Surefire levanta uma JVM por core e cria uma
%% pool de 5 threads em cada JVM para executar testes em paralelo.}

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Configuration \ForkParMeth{} on Maven.}
\end{figure}

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
With this configuration, Maven~---~through its test plugin
Surefire~\cite{maven-surefire-plugin}~---~forks one JVM per core
(\CodeIn{forkCount} parameter) and uses five threads
(\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
parameter) within each forked JVM.
